---
title: "Assignment 5"
author: "Anthony Criscione"
date: "9/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(here)
```


## 1. Reading Data
```{r}
path <- here("Datasets", "netflix_titles.csv")
netflix <- read_csv(path,
                    col_types = cols(
                      show_id = col_double(),
                      type = col_factor(), # Changed char->factor
                      title = col_character(),
                      director = col_character(),
                      cast = col_character(),
                      country = col_character(),
                      date_added = col_date(format = "%B %d, %Y"), # Changed char->date
                      release_year = col_date(format = "%Y"), # Changed dbl->date
                      rating = col_factor(), # Changed char->factor
                      duration = col_number(), # Changed char->number
                      listed_in = col_character(),
                      description = col_character()
                    )
)
```

For reading the Netflix data, I changed `type` from character to factor since there are only 2 types, *Movie* and *TV Show*. I also changed the date variables (`date_added` and `release_year`) from character and double (respectively) to dates with the proper formatting. Finally, I changed `rating` from character to factor (since there are a relatively small number of pre-defined ratings), and `duration` from character to number to parse out the digits (movies have durations like "90 min" and shows have durations like "1 Season").


## 2. EDA: Duration
```{r}
netflix %>%
  filter(type == "Movie") %>%
  ggplot(aes(duration)) +
  geom_histogram(binwidth = 20) +
  labs(title = "Durations of Netflix Movies",
       x = "Duration (minutes)", y = "Count")
```

This analysis shows distribution of durations of movies. Since this data set contains both movies and TV shows, the TV shows had to be filtered out (their durations are measured in seasons instead of minutes and cannot be converted). Overall, the movie durations follow a fairly normal distribution, with movies around 100 minutes being the most common. Notably, there appear to be more short movies (duration < 50 minutes) than there are long movies (duration > 160 minutes).


## 3. Covariation: Type by Country
```{r}
netflix %>%
  mutate(US_Content = grepl("United States", country)) %>%
  ggplot(aes(type, fill = US_Content)) +
  geom_bar(position = "dodge") +
  labs(title = "Distribution of Type In & Out of US",
       x = "Type", y = "Count")
```

For covariation, I decided to explore different content types available by country (to simplify, I went with US vs. Non-US content). Overall, there is more content outside of the US than there is inside the US, but considering this is comparing many countries to one, the US certainly has a *lot* of content on its own. Looking at the differences between the two, the US has almost as many movies as the rest of the world (within roughly 300 movies), but only half as many TV shows as the rest of the world. Notice that the rest of the world has a show-to-movie ratio of about 1:2, while the US is roughly 1:3. The US seems to value movies more than TV shows compared to the rest of the world.

For data cleaning, I needed to separate content by whether or not it was available in the US. Since some content is available in multiple countries (i.e. `country = "China, Canada, United States"`), I couldn't use `filter(country == "United States")`, and therefore had to use `grepl()` to find the substring "United States" (`grepl` is a grep function, which uses regular expressions). I'm not sure if there is a more R-typical way of finding substrings, but this worked nicely. I used `mutate` to create an additional column for this grouping so the key in the plot would show `US_Content` instead of `grepl("United States", country)`.